\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-10-11 calendar-vis.Rmd
re-compile manuscript

Figure \@ref(fig:dow) shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two children, uses more energy over the weekdays than other households. The relatively larger boxes for household 2 indicate greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the weekdays, reflecting work and leisure patterns.

@@

(ref:calendar-elec-cap) Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February.

>>>>

Figure \@ref(fig:dow) shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two children, uses more energy over the weekdays than other households. The relatively larger boxes for household 2 indicate greater variability in daily energy consumption with noticeable variations on Fridays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the weekdays, reflecting work and leisure patterns.

@@

(ref:calendar-elec-cap) Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February. Note that April 30 is wrapped to the start of the month.

### 2019-10-11 calendar-vis.tex
re-compile manuscript

Figure \ref{fig:dow} shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two children, uses more energy over the weekdays than other households. The relatively larger boxes for household 2 indicate greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the weekdays, reflecting work and leisure patterns.

@@

\caption{Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February.}\label{fig:calendar-elec}
\end{figure}

>>>>

Figure \ref{fig:dow} shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two children, uses more energy over the weekdays than other households. The relatively larger boxes for household 2 indicate greater variability in daily energy consumption with noticeable variations on Fridays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the weekdays, reflecting work and leisure patterns.

@@

\caption{Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February. Note that April 30 is wrapped to the start of the month.}\label{fig:calendar-elec}
\end{figure}
